The Unicode Cookbook \linebreak for Linguists

### 2018-06-11 book/chapters/orthography_profiles.tex
closes #31

	\item \textsc{Metadata should be added in a separate UTF-8 text file} using 
	   the JSON-LD dialect specified in \textit{Metadata Vocabulary for Tabular 
	   Data}.\footnote{\url{https://www.w3.org/TR/tabular-metadata/}} This metadata 
	   format allows for easy inclusion of Dublin Core metadata,\footnote{\url{http://dublincore.org/}} 
	   which should be used to specify information about the orthographic description 
	   in the orthography profile.\footnote{\url{http://w3c.github.io/csvw/metadata/#dfn-common-property}} 
	   The orthography profile metadata should minimally include provenance information including: 
	   (i) author, (ii) date, (iii) title of the profile, and (iv)
       bibliographic data for resource(s) that illustrate the orthography
       described in the profile. Crucially, the metadata should also specify 
	   (v) a stable language identifier of the target language of the profile
       using BCP 47/ISO 639-3 or Glottocode as per the CLDF ontology.\footnote{\url{http://cldf.clld.org/v1.0/terms.rdf}}	   	   
	   Further, the metadata file should provide information about the orthography profile's structure and contents, 
	   including: (vi) its dialect description,\footnote{\url{http://w3c.github.io/csvw/metadata/#dfn-dialect-descriptions}} 
	   (vii) the tokenization method (see below), and (ix) proper column           
	   descriptions,\footnote{\url{http://w3c.github.io/csvw/metadata/#dfn-datatype-description}} 
	   which describe how a column should be interpreted and processed (e.g.\ whether they 
	   should be processed as regular expressions; see below).
	   Finally, in accordance with the \textit{Metadata Vocabulary for Tabular 
	   Data}, the metadata's filename should consist of the orthography 
	   profile's filename appended with ``-metadata.json''.\footnote{JSON-LD metadata 
	   is also the choice for datasets conforming to the Cross-Linguistic Data Formats standard, 
	   see: \url{http://cldf.clld.org/}.}

>>>>

	\item \textsc{Metadata should be added in a separate utf-\scalebox{0.8}{8} text file} using 
	   the JSON-LD dialect specified in \textit{Metadata Vocabulary for Tabular 
	   Data}.\footnote{\url{https://www.w3.org/TR/tabular-metadata/}} This metadata 
	   format allows for easy inclusion of Dublin Core metadata,\footnote{\url{http://dublincore.org/}} 
	   which should be used to specify information about the orthographic description 
	   in the orthography profile.\footnote{\url{http://w3c.github.io/csvw/metadata/#dfn-common-property}} 
	   The orthography profile metadata should minimally include provenance information including: 
	   (i) author, (ii) date, (iii) title of the profile, and (iv)
       bibliographic data for resource(s) that illustrate the orthography
       described in the profile. Crucially, the metadata should also specify 
	   (v) a stable language identifier of the target language of the profile
       using BCP 47/ISO 639-3 or Glottocode as per the CLDF ontology.\footnote{\url{http://cldf.clld.org/v1.0/terms.rdf}}	   	   
	   Further, the metadata file should provide information about the orthography profile's structure and contents, 
	   including: (vi) its dialect description,\footnote{\url{http://w3c.github.io/csvw/metadata/#dfn-dialect-descriptions}} 
	   and (vii) proper column descriptions,\footnote{\url{http://w3c.github.io/csvw/metadata/#dfn-datatype-description}} 
	   which describe how a column should be interpreted and processed (e.g.\ whether they 
	   should be processed as regular expressions; see below).
	   Finally, in accordance with the \textit{Metadata Vocabulary for Tabular 
	   Data}, the metadata's filename should consist of the orthography 
	   profile's filename appended with ``-metadata.json''.\footnote{JSON-LD metadata 
	   is also the choice for datasets conforming to the Cross-Linguistic Data Formats standard, 
	   see: \url{http://cldf.clld.org/}.}
